---
title: "CS422 Section 01"
author: "Kaiyue Ma"
output: html_document
---

```{r}
rm(list=ls())
```

```{r}
library(textreuse)
library(dplyr)
library(proxy)
library(stringr)
library(data.table)
library(tidyr)
library(plyr)
library(reshape)
library(lsa)

setwd("/Users/michael/Codes/R/4")
```

# 2.1
```{r}
movies <- read.csv("movies.csv")
ratings <- read.csv("ratings.csv")
```

```{r}
length(unique(movies$movieId))
length(unique(ratings$movieId))

dim(movies[which(!movies$movieId %in% ratings$movieId),])
dim(ratings[which(!ratings$movieId %in% movies$movieId),])

```

```{r}
for(i in unique(ratings$userId))
  {
    filename <- paste("user",i,".txt",sep = " ")
    movieIDs <- ratings[which(ratings$userId == i),"movieId"]
    movnames <- movies[match(movieIDs,movies$movieId),"title"]
    writeLines(as.character(movnames),filename)
    
  }

files <- list.files("/Users/michael/Codes/R/4", full.names = T)

corpus <- TextReuseCorpus(files, tokenizer = tokenize_ngrams, n = 5, keep_tokens = T)
```

## 2.1 (a)
```{r}
corpus %>%
  tokens %>%
  unlist %>%
  unique %>%
  length

```
```{r}
corpus %>%
  length
```
#### There are 333583 rows and 671 columns in the characteristic matrix.

## 2.1 (b)
```{r}
d <- corpus[["user 20 "]]
```

#2.1 (b) (i)
```{r}
str_count(d$content,"\n")
```
#### User 20 rated 98 (97+1) movies
#2.1 (b) (ii)
#### The first 5 shingles are:
```{r}
d$tokens[1:5]
```

## 2.1 (c)
```{r}
pcomp <- pairwise_compare(corpus, jaccard_similarity)
pcan <- pairwise_candidates(pcomp)
```

### 2.1 (c) (i)
```{r}
summary(pcan$score >= 0.6)
```
#### There are 0 user.

### 2.1 (c) (ii)
```{r}
summary(pcan$score >= 0.5)
```
#### There are 0 user.

### 2.1 (c) (iii)
```{r}
summary(pcan$score >= 0.4)
```
#### There are 4 users.

### 2.1 (c) (iv)
#### Those 4 users are:
```{r}
pcan[which(pcan$score>=0.40),]
```
#### user 151	user 369
#### user 191	user 317
#### user 191	user 513
#### user 225	user 375
## 2.1 (d)
### 2.1 (d) (i)
```{r}
lsh_probability(h = 100, b = 20, s = 0.6)
lsh_probability(h = 115, b = 23, s = 0.6)
lsh_probability(h = 120, b = 30, s = 0.6)
```
#### Taking 120 as number of minhash signatures and 30 as number of bands.

### 2.1 (d) (ii)
```{r}
minhash <-minhash_generator(n = 120, seed = 100)
new_corpus <- TextReuseCorpus(files,tokenizer = tokenize_ngrams, n = 5,keep_tokens = TRUE,minhash_func = minhash)
```
#### The first five minhashes are:
```{r}
d1 <- new_corpus[["user 20 "]]
cat("- \n")
d1$minhashes[1:5]
```

## 2.1 (e)
```{r}
buckets1 <- lsh(new_corpus,bands= 30)
candidates <- lsh_candidates(buckets1)
result <- lsh_compare(candidates, new_corpus, jaccard_similarity)
```

### 2.1 (e) (i)
```{r}
result[which(result$score <= 0.60 & result$score>=0.50),]
```
#### No. There should not be candidates pair(s) whose similarity between 0.60 and 0.50, because in brute force comparison is accuracy. Tht brute froce comparison compares with every possible combination does not yeild any similarity then this method should not yield any results of similarity.

### 2.1 (e) (ii)
#### Users whose similarity score at least 0.40 are:
```{r}
result[which(result$score >= 0.40),]
```

### 2.1 (e) (iii)
#### No, LSH lost 2 pairs' similarity which are over 0.4.

### 2.1 (e) (iv)
```{r}
((1 - 59 / 228826) * 100) %>%
  round(3) %>%
  paste("%") %>%
  print
```
#### There are 228826 comparisons and 59 comparisons. Generated 99.974% of work was saved.

# 2.2
```{r}
print("The user number is:")
20407079%%671
#recommendation for 627
```

```{r}
#movieID--user627
user627_movieID <-ratings[ratings$userId==627,"movieId"]

# movie ID and genre of user627
user627_movieID_genre <- movies[match(user627_movieID,movies$movieId),c("movieId","genres")]
user627_movieID_genre$genres <- trimws(user627_movieID_genre$genres,which ="both")

temp <-strsplit(as.character(user627_movieID_genre$genres), split = "|", fixed = T)
temp <- ldply(temp,rbind)


#temp user
user627_movieID_genre <- cbind(user627_movieID_genre,temp)
user627_movieID_genre <- user627_movieID_genre[,-2]

x <- melt(user627_movieID_genre,id.vars = c("movieId"))
x <- x[order(x$movieId),]  

x <- x[-which(is.na(x$value)),]
x <- x[,-2]

###############################################################
#creating user profile
user_profile <- data.frame(recast(x, movieId~value,id.var = c("movieId","value")))
user_profile$`(no genres listed)` <- NA


user_profile[,2:ncol(user_profile)] <- sapply(user_profile[,2:ncol(user_profile)], as.character)
user_profile[is.na(user_profile)] <- 0

user_profile <- data.frame(lapply(user_profile, function(x) as.numeric(x!=0)))

user_profile$movieId <- user627_movieID_genre$movieId

user_profile <- user_profile[,c(1,2,3,4,5,6,7,8,9,14,15,10,19,16,11,17,12,13,18,20,21)]

rownames(user_profile) <- user_profile$movieId
```

```{r}
#creating the movie profile dataframe

set.seed(3)
rand_mov <- sample(1:nrow(movies),10)
movies_temp <- movies[rand_mov, c("movieId","genres")]


temp1 <- strsplit(as.character(movies_temp$genres), split = "|", fixed = T)
temp1 <- ldply(temp1,rbind)

movies_temp <- cbind(movies_temp,temp1)
movies_temp <- movies_temp[,-2]


y <- melt(movies_temp,id.vars = c("movieId"))
y <- y[order(y$movieId),]  
y <- y[-which(is.na(y$value)),]
y <- y[,-2]

movie_profile <- data.frame(recast(y, movieId~value,id.var = c("movieId","value")))
movie_profile[,2:ncol(movie_profile)] <- sapply(movie_profile[,2:ncol(movie_profile)], as.character)

movie_profile$Children <- NA
movie_profile$Crime <- NA
movie_profile$Documentary <- NA
movie_profile$Fantasy <- NA
movie_profile$`Film-Noir` <- NA
movie_profile$IMAX <- NA
movie_profile$Musical <- NA
movie_profile$`(no genres listed)` <- NA

movie_profile[is.na(movie_profile)] <- 0

movie_profile <- data.frame(lapply(movie_profile, function(x) as.numeric(x!=0)))

movie_profile$movieId <- movies_temp$movieId

movie_profile <- movie_profile[,c(1,2,8,3,14,4,15,16,5,17,21,6,18,19,12,7,13,9,10,11,20)]
rownames(movie_profile) <- movie_profile$movieId

user_prof_mat <- as.matrix(user_profile[,2:ncol(user_profile)])

movie_prof_mat <- as.matrix(movie_profile[,2:ncol(movie_profile)])

```

```{r}
# #cosine
# mycosine <- function(x,y){
#      c <- sum(x*y) / (sqrt(sum(x*x)) * sqrt(sum(y*y)))
#      return(c)
#  }
# 
# trial <- matrix(NA,ncol = nrow(user_prof_mat),nrow = nrow(movie_prof_mat))
# 
# #similarity
# for (i in 1:nrow(user_prof_mat)) {
# 
#   for (j in 1:nrow(movie_prof_mat)) {
# 
#     trial[j,i] <- mycosine(user_prof_mat[i,],movie_prof_mat[j,])
# 
#   }
# 
# }

user_profile.avg <- colSums(user_profile[,2:ncol(user_profile)])/nrow(user_prof_mat)

cos.simi <- cosine(user_profile.avg, movie_profile[,2:ncol(movie_profile)] %>% as.matrix %>% t) %>%
  sort(decreasing = TRUE) %>%
  round(3)
recommend <- names(cos.simi)[1:10]

```

```{r}
recc_title <-as.character(movies[match(recommend,movies$movieId),"title"])

# recc_simi <- c(max(trial[1,]),max(trial[2,]),max(trial[3,]),max(trial[4,]),max(trial[5,]),max(trial[6,]),max(trial[7,]),max(trial[8,]),max(trial[9,]),max(trial[10,]))

```

```{r}
print("The Movies recommended for User627 are: ")
for (i in 1:10) {
  
  print(paste0("The movie ", recc_title[i]," has similarity score of ", cos.simi[i]))
  
}


```

# 2.3
## 2.3 (a)
```{r}
ratings <- data.table(ratings)
id191 <- 191
movie3 <- ratings[userId == id191, movieId]
test3 <- c(150, 296, 380, 590)
trainer3 <- setdiff(movie3, test3)
jac.simi <- c(0.4358974, 0.4033613, 0.3255814, 0.3049645, 0.2753623,0.2727273, 0.2527473, 0.2420382, 0.2262774, 0.2216216, 0.2105263, 0.2009804)
names(jac.simi) <- c(513, 317, 415, 375, 64, 556, 82, 225, 657, 266, 568, 50)
```

```{r}
set.seed(233)
user3 <- sample(jac.simi, 5)
```

```{r}
user191_rating <- ratings[ratings$userId == 191, c("movieId","rating")]

user64_rating <- ratings[ratings$userId == 64, c("movieId","rating")]
user266_rating <- ratings[ratings$userId == 266, c("movieId","rating")]
user657_rating <-ratings[ratings$userId == 657, c("movieId","rating")]
user225_rating <- ratings[ratings$userId ==225, c("movieId","rating")]
user375_rating <-  ratings[ratings$userId == 375, c("movieId","rating")]

intersect_64 <- intersect(user64_rating$movieId, user191_rating$movieId)
intersect_266 <- intersect(user266_rating$movieId, user191_rating$movieId)
intersect_657 <- intersect(user657_rating$movieId, user191_rating$movieId)
intersect_225 <- intersect(user225_rating$movieId, user191_rating$movieId)
intresect_375 <- intersect(user375_rating$movieId, user191_rating$movieId)

temp2 <- rbind(user191_rating, user64_rating[match(intersect_64, user64_rating$movieId),], user266_rating[match(intersect_266, user266_rating$movieId),], user657_rating[match(intersect_657, user657_rating$movieId), ], user225_rating[match(intersect_225, user225_rating$movieId), ], user375_rating[match(intresect_375, user375_rating$movieId), ])

nrow(user191_rating)
nrow(user64_rating[match(intersect_64, user64_rating$movieId), ])
nrow(user266_rating[match(intersect_266, user266_rating$movieId), ])
nrow(user657_rating[match(intersect_657, user657_rating$movieId), ])
nrow(user225_rating[match(intersect_225, user225_rating$movieId), ])
nrow(user375_rating[match(intresect_375, user375_rating$movieId), ])

temp2[c(1:29),"UserID"] <- 191
temp2[c(30:46),"UserID"] <- 64
temp2[c(47:66),"UserID"] <- 266
temp2[c(67:81),"UserID"] <- 657
temp2[c(82:100), "UserID"] <- 225
temp2[c(101:119),"UserID"] <- 375



z <- melt(temp2, id.vars = c("movieId","UserID"), na.rm = F)

U <-data.frame(cast(z, UserID~variable+movieId))
rownames(U) <- U$UserID
colnames(U) <- gsub("rating_", "", colnames(U))
U <- U[,-1]

true.rating <- U[which(rownames(U) == id191), which(colnames(U) %in% test3)]

U[which(rownames(U) == id191), which(colnames(U) %in% test3)] <- NA
U[is.na(U)] <- 0

```

```{r}
neighbor3 <- sort(user3, decreasing = TRUE)[1:3]
neighbor3 <- neighbor3[order(as.numeric(names(neighbor3)))]
R <- U[rownames(U) %in% names(neighbor3), colnames(U) %in% test3]
R <- R[order(as.numeric(rownames(R))), ]
pred <- as.vector(t(neighbor3) %*% as.matrix(R) / sum(neighbor3))
RMSE <- sqrt(sum((pred - true.rating)^2) / length(pred))
1:length(test3) %>%
  sapply(function(x) {
    paste0(test3[x], ": ", round(pred[x], 3))
  }) %>%
  paste0(collapse = "\t\n") %>%
  paste0("User ID ", id191, ", ", length(user3), " random user IDs: ", paste0(names(user3), collapse = ", "), ".\t\nUsing user-user similarity, User ID ", id191, " will rate the movies as follows: \t\n", .,
         "\t\nRMSE: ", RMSE) %>%
  cat
```

## 2.3 (b)
```{r}

findMovie <- function(data) {
  d <- data.frame(data$rating) %>% t
  colnames(d) <- data$movieId
  rownames(d) <- data$userId[1]
  return(d)
}

Ut <- c(names(user3), id191) %>%
  sapply(function(x) {
    ratings[userId == x, findMovie(.SD), .SDcols = c("rating", "movieId", "userId")]
  }) %>%
  melt %>%
  dcast(X1 ~ X2) %>%
  t
colnames(Ut) <- Ut[1, ]
Ut <- Ut[-1, ]
Ut <- Ut[which(rownames(Ut) %in% movie3), ]

cos.simi3 <- apply(Ut, 2, function(x) {
  n <- sum(!is.na(x))
  x <- ifelse(is.na(x), 0, x)
  x - sum(x) / n
}) %>%
  t %>%
  cosine


pred3 <- test3 %>%
  sapply(function(x) {
    neighbor <- cos.simi3[row.names(cos.simi3) == x, colnames(cos.simi3) %in% trainer3] %>%
      sort(decreasing = TRUE) %>%
      names()
    neighbor <- neighbor[1:3]
    ref <- Ut[rownames(Ut) %in% neighbor, colnames(Ut) == id191]
    ref <- ref[order(as.numeric(names(ref)))]
    cos.neighbor <- cos.simi3[row.names(cos.simi3) == x, colnames(cos.simi3) %in% neighbor]
    cos.neighbor <- cos.neighbor[order(as.numeric(names(cos.neighbor)))]
    pred <- sum(ref * cos.neighbor) / sum(cos.neighbor)
    return(pred)
  })

RMSE3 <- sqrt(sum((pred3 - true.rating)^2) / length(pred))
1:length(test3) %>%
  sapply(function(x) {
    paste0(test3[x], ": ", round(pred3[x], 3))
    }) %>%
  paste0(collapse = "\t\n") %>%
  paste0("User ID ", id191, ", ", length(user3), " random user IDs: ", paste0(names(user3), collapse = ", "), ".\t\nUsing user-user similarity, User ID ", id191, " will rate the movies as follows: \t\n", .,
"\t\nRMSE: ", RMSE3) %>%
  cat

```


